CudeleFS: Programmable Consistency and \\Durability in a Global Namespace

### 2017-04-03 paper/sections/1_introduction.tex
paper: update graphs and scan evaluation
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What did we do
We propose a subtree policy API that lets future programmers control
the consistency and durability for subtrees in the file system namespace. For performance, one
subtree can adopt weaker consistency semantics while another subtree can retain
the rigidity of POSIX's strong consistency. Figure~\ref{fig:subtree-policies}
shows an example setup where a single global namespace has directories for
applications designed for different, state-of-the-art HPC architectures.  We
present Cudele, a prototype programmable file system that supports different
degrees of consistency and durability by exposing mechanisms used within the
file system as a client library.  CudeleFS supports 3 forms of consistency
(invisible, weak, and strong) and 3 degrees of durability (none, local, and
global) giving the user a wide range of policies and optimizations
that can be custom fit to an application. Our contributions:

@@

  \item an apples-to-apples comparison of the strategies used in recently proposed research systems against
  previously unexplored metadata designs, all implemented using Cudele.

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.
Section~\ref{sec:posix-overheads} quantifies the cost of POSIX
consistency and system-defined durability and
Section~\ref{sec:methodology-decoupled-namespaces} presents the Cudele
prototype and API. Section~\ref{sec:implementation} describes Cudele's
mechanisms and shows how re-using internal subsystems results in an
implementation of less than 500 lines of code. The evaluation in
Section~\ref{sec:evaluation} quantifies the overheads and performance gains of
explored and previously unexplored metadata designs.
Section~\ref{sec:related-work} places CudeleFS in the context of other related
work.

>>>>

% What did we do
We propose a subtree policy API that lets future programmers control
the consistency and durability for subtrees in the file system namespace. For performance, one
subtree can adopt weaker consistency semantics while another subtree can retain
the rigidity of POSIX's strong consistency. Figure~\ref{fig:subtree-policies}
shows an example setup where a single global namespace has directories for
applications designed for different, state-of-the-art HPC architectures.  We
present CudeleFS, a prototype programmable file system that supports different
degrees of consistency and durability by exposing mechanisms used within the
file system as a client library.  CudeleFS supports 3 forms of consistency
(invisible, weak, and strong) and 3 degrees of durability (none, local, and
global) giving the user a wide range of policies and optimizations
that can be custom fit to an application. Our contributions:

@@

  \item an apples-to-apples comparison of the strategies used in recently proposed research systems against
  previously unexplored metadata designs, all implemented using CudeleFS.

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.
Section~\ref{sec:posix-overheads} quantifies the cost of POSIX
consistency and system-defined durability and
Section~\ref{sec:methodology-decoupled-namespaces} presents the CudeleFS
prototype and API. Section~\ref{sec:implementation} describes the CudeleFS
mechanisms and shows how re-using internal subsystems results in an
implementation of less than 500 lines of code. The evaluation in
Section~\ref{sec:evaluation} quantifies the overheads and performance gains of
explored and previously unexplored metadata designs.
Section~\ref{sec:related-work} places CudeleFS in the context of other related
work.

### 2017-04-03 paper/sections/3_posix_overheads.tex
partial
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: update graphs and scan evaluation
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and
CPU utilization because of the consistency and durability demands of
CephFS.}\label{fig:overhead-creates}
\end{figure}

@@

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./figures/journal.png} 
\caption{CephFS uses a journal to stage updates and tracks dirty metadata in
the collective memory of the metadata servers. Each metadata server maintains its own journal, which is
broken up into 4MB segments. These segments are pushed into RADOS and deleted
when that particular segment is trimmed from the end of the log. In addition to
journal segments, RADOS also stores per-directory objects. \label{fig:journal}}
\end{figure}
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{Journal Segment Size} \label{fig:slowdown-journal-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-journal.png}
      \caption{180MB Segment vs. No Journal}
      \label{fig:slowdown-journal-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-cache.png}
      \caption{Inode Cache}
      \label{fig:slowdown-journal-c}
  \end{subfigure}
  \caption{The overhead of the file system metadata journal. The segment size
  is the threshold that the metadata server starts
  trimming.\label{fig:slowdown-journal}}
\end{figure*}

% - sequential IO, trim redundant operations
\noindent\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store, similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL}, grows to large extents which
allows to (1) sequentially write into the object store and (2) provide the ability for daemons to
trim redundant or irrelevant journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

% purpose of the journal
As shown in Figure~\ref{fig:journal}, in addition to the metadata journal,
CephFS also stores metadata in RADOS, where directories
and their file inodes are stored as objects.  The metadata server applies the
updates in the journal to this metadata store when the journal reaches a certain
size. The metadata store is optimized for recovery ({\it i.e.} reading) while
the metadata journal is write-optimized.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-interfere.png}
      \caption{Inteference forces \texttt{lookup()}s}
      \label{fig:interfere-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere.png}
      \caption{Interference hurts performance}
      \label{fig:interfere-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-types.png}
      \caption{Different interferring requests}
      \label{fig:interfere-c}
  \end{subfigure}
  \caption{When a client create stream is ``isolated" lookups resolve
  locally; but when a second client ``interferes" by creating in the same
  directory, the directory inode capability is revoked forcing all clients to
  centralize lookups at the metadata server.
  \label{fig:interfere}}
\end{figure*}

>>>>

@@

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./figures/journal.png} 
\caption{CephFS uses a journal to stage updates and tracks dirty metadata in
the collective memory of the metadata servers. Each metadata server maintains its own journal, which is
broken up into 4MB segments. These segments are pushed into RADOS and deleted
when that particular segment is trimmed from the end of the log. In addition to
journal segments, RADOS also stores per-directory objects. \label{fig:journal}}
\end{figure}
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{Journal Segment Size} \label{fig:slowdown-journal-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-journal.png}
      \caption{180MB Segment vs. No Journal}
      \label{fig:slowdown-journal-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-cache.png}
      \caption{Inode Cache}
      \label{fig:slowdown-journal-c}
  \end{subfigure}
  \caption{The overhead of global durability in CephFS. The segment size
  is the threshold that the metadata server starts
  trimming.\label{fig:slowdown-journal}}
\end{figure*}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-interfere.png}
      \caption{Inteference forces \texttt{lookup()}s}
      \label{fig:interfere-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere.png}
      \caption{Interference hurts performance}
      \label{fig:interfere-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-types.png}
      \caption{Different interferring requests}
      \label{fig:interfere-c}
  \end{subfigure}
  \caption{The overhead of strong consistency in CephFS. When a second client
  ``interferes", capabilities are revoked and metadata servers do more work.
  \label{fig:interfere}}
\end{figure*}

### 2017-04-03 paper/sections/5_implementation.tex
paper: update graphs and scan evaluation
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\noindent\textbf{Cudele}: ``Nonvolatile Apply" uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.\\

@@

\noindent\textbf{Cudele}: uses the large inodes to store consistency and
durability policies in the directory inode. This approach uses the File Type
interface from the Malacology programmable store
system~\cite{sevilla:eurosys17} and it tells clients how to access the
underlying metadata. The underlying implementation stores executable code in
the inode that calls the different CudeleFS mechanisms. Of course, there are many
security and access control aspects of this approach but that is beyond the
scope of this paper.

>>>>

\noindent\textbf{CudeleFS}: ``Nonvolatile Apply" uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.\\

@@

\noindent\textbf{CudeleFS}: uses the large inodes to store consistency and
durability policies in the directory inode. This approach uses the File Type
interface from the Malacology programmable store
system~\cite{sevilla:eurosys17} and it tells clients how to access the
underlying metadata. The underlying implementation stores executable code in
the inode that calls the different CudeleFS mechanisms. Of course, there are many
security and access control aspects of this approach but that is beyond the
scope of this paper.

### 2017-04-03 paper/sections/6_results.tex
paper: update graphs and scan evaluation
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We evaluate CudeleFS on a 15 node cluster, partitioned into 8 object storage
servers, 3 metadata servers, and 2 monitor servers. The object storage servers
double as clients which is fine because clients are CPU and memory bound while
object storage servers are disk IO bound. All daemons run as a single process
which is the default setting for Ceph and the nodes have 2 dual core 2GHz
processors with 8GB of RAM. There are three daemons per object storage server
(one for each disk formatted with XFS) and they share an SSD for the journal.
The nodes are running Ubuntu 12.04.4, kernel version 3.2.0-63 but all
experiments run in Docker containers; this makes it easier to tear down and
re-initialize ({\it e.g.}, dropping the kernel cache) for the cluster between
experiments.

@@

Figure~\ref{fig:slowdown-mechanisms} shows the runtime of the Cudele
mechanisms, normalized to the time it takes to write 100K file create updates
to the client's in-memory journal ({\it i.e.} the create mechanism). Bars above
\(10^0\) are slower than the create mechanism and bars below are faster.
``Stream" is an approximation of the overhead and is calculated by subtracting
the runtime of the job with the journal turned off from the runtime with the
journal turned on. All the slowdowns and speedups reported are for the 100K
file create job, the largest workoad we tested.

% RPCs vs. apply: calls to metadata server vs. RADOS
\subsubsection{Overhead of RPCs} ``RPCs" is \(66\times\) slower than ``volatile
apply" because sending individual metadata updates over the network is costly.
While ``RPCs" sends a request for every file create, ``nonvolatile apply"
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (``nonvolatile apply") is \(10\times\) slower.

% TODO: why is apply so slow.  
% apply: no CephFS changes, pulls/pushes same RADOS obj.
% v_apply vs. apply/persist: communicating through RADOS
\subsubsection{Overhead of ``nonvolatile apply"} The cost of ``nonvolatile
apply" is much larger than all the other mechanisms.  That mechanism was not
implemented as part of CudeleFS -- it was a debugging and recovery tool packaged
with CephFS. It works by iterating over the updates in the journal and pulling
all objects that {\it may} be affected by the update.  This means that two
objects are repeatedly pulled, updated, and pushed: the object that houses the
experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  The cost of communcating through the object store is shown
by comparing the runtime of ``volatile apply" + ``global persist" to
``nonvolatile apply". These two operations end up with the same final metadata
state but using ``nonvolatile apply" is clearly inferior.

% persist vs. save: one disk vs. many
\subsubsection{Parallelism of the Object Store} Comparing ``local" and ``global
persist" demonstrates the bandwidth advantages of storing the journal in a
distributed object store. As the journal size increases, the ``global persist"
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the size of the object store can help mitigate the overheads of
globally persisting metadata updates.

\subsubsection{Journal Size} Figure~\ref{fig:behavior-journal-size} shows the
amount of storage per journal update (\(y\) axis) for the range of file creates
we tested (\(x\) axis). The increase in file size is linear with the number of
metadata creates and suggests that updates for a million files would be
\(2.5\text{KB}*1\text{ million files} = 2.38\text{GB}\). Transfer times for
files this large on an HPC network are reasonable.

@@

Figure~\ref{fig:slowdown-strong-weak} shows the runtimes of weak and
strong consistency based systems implemented on Cudele, normalized to the
runtime of the create mechanism (again, just creating files in the client's
in-memory journal). We scaled the number of files up to 100K which is the
maximum size of a directory by default in CephFS. We use the following
compositions from the mechanisms in Table~\ref{table:spectrum}:

\begin{itemize}
  \item Strong Consistency
  \begin{itemize}
    \item[]  \texttt{RPCs} \(+\) \texttt{stream}
  \end{itemize}
  \item Strong Consistency, No Fault Tolerance
  \begin{itemize}
    \item[] \texttt{RPCs}
  \end{itemize}
  \item Weak Consistency
  \begin{itemize}
    \item[] \texttt{creates} \(+\) \texttt{local persist}
  \end{itemize}
  \item Weak Consistency, No Fault Tolerance
  \begin{itemize}
    \item[] \texttt{creates} \(+\) \texttt{local persist} \(+\) \texttt{volatile apply}
  \end{itemize}
\end{itemize}

@@

% POSIX (no stream) vs. POSIX: cost of durability < consistency
\subsubsection{Durability \(<<\) Consistency} The \(1.15\times\) overhead of
``Strong Consistency" compared to ``Strong Consistency, No Fault Tolerance" for
100K files is neglible. It suggests that the overhead of consistency is much
larger than the overhead of durability. This conclusion should be stronger as
we scale the number of files because the cost of streaming the journal into the
object store is constant. We omit the same analysis for ``Weak Consistency"
because the runtimes are so short that the normalized slowdowns are misleading.

% Weak Consistency benefit not due to metadata format
\subsubsection{Metadata Formats} Because the metadata formats are the same for
all schemes we argue that the performance gain for decoupled namespaces comes
from relaxing the consistency guarantees and not from the metadata formats, as
was argued in previous work outlining the benefit of
SSTables~\cite{ren:atc2013-tablefs, ren:sc2014-indexfs}.

@@

% setup: 2cs sep dirs, 2cs DN, 1c malicious write
Next we show how CudeleFS can be programmed to block interferring clients. We
use the same problematic workload from Figure~\ref{fig:interfere-b}, where
clients write to their own private directories and another client interferes at
30 seconds.  We also have another client write to a decoupled namespace and
merge its updates at 90 seconds.  We equip each client directory with the
configuration in Listing~\ref{src:block}.  Each directory functions with RPCs
and stream enabled -- which is the default implementation of CephFS. The only
difference is that we enable blocking on each subtree so while the tree behaves
like CephFS, all interferring operations will be returned with \texttt{-EBUSY}.
Note that IndexFS does a similar operation with leases except clients block.

% results
The benefits of this isolations are shown next to the bars from
Figure~\ref{fig:interfere-b} in Figure~\ref{fig:slowdown-allow-block}. Because
\{``allow", ``block"\} has the same performance as \{``interfere",
``isolated"\}, we draw the following three conclusions: (1) clients that use the
API to block interferring clients  get the same performance as isolated
clients, (2) there is a neglible effect on performance for the extra work the
metadata server does to return \texttt{-EBUSY}, and (3) merging updates from
the decoupled client has a neglible effect on performance.\\

\noindent\textbf{Takeaway}: the API is sufficient for isolating performance
when applications require it. This is a way of controlling consistency.

@@

\subsection{Cost of Nonvolatile Apply}
% Why so slow?
Creating many files in the same directory would touch the same object but the
existing implementation results in this object being repeatedly pushed/pulled.

>>>>

We evaluate CudeleFS on a 15 node cluster, partitioned into 8 object storage
servers, 3 metadata servers, and 2 monitor servers. The object storage servers
double as clients which is fine because clients are CPU and memory bound while
object storage servers are disk IO bound. All daemons run as a single process
which is the default setting for Ceph and the nodes have 2 dual core 2GHz
processors with 8GB of RAM. There are three daemons per object storage server
(one for each disk formatted with XFS) and they share an SSD for the journal.
The nodes are running Ubuntu 12.04.4, kernel version 3.2.0-63 but all
experiments run in Docker containers; this makes it easier to tear down and
re-initialize the cluster ({\it e.g.}, dropping the kernel cache) between
experiments.

@@

Figure~\ref{fig:slowdown-mechanisms} shows the runtime of the CudeleFS
mechanisms, normalized to the time it takes to write 100K file create updates
to the client's in-memory journal ({\it i.e.} the ``Create" mechanism). Bars
above \(10^0\) are slower than the ``Create" mechanism and bars below are
faster.  ``Stream" is an approximation of the overhead and is calculated by
subtracting the runtime of the job with the journal turned off from the runtime
with the journal turned on. All the slowdowns and speedups reported are for the
100K file create job, the largest workoad we tested\footnote{We stopped testing
at 100K because this is the maximum recommended size of a directory in CephFS;
preliminary experiemnts with larger directory sizes show memory problems.}.

% RPCs vs. apply: calls to metadata server vs. RADOS
\subsubsection{Overhead of RPCs} ``RPCs" is \(66\times\) slower than ``Volatile
Apply" because sending individual metadata updates over the network is costly.
While ``RPCs" sends a request for every file create, ``Nonvolatile Apply"
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (``Nonvolatile Apply") is \(10\times\) slower.

% TODO: why is apply so slow.  
% apply: no CephFS changes, pulls/pushes same RADOS obj.
% v_apply vs. apply/persist: communicating through RADOS
\subsubsection{Overhead of ``Nonvolatile Apply"} The cost of ``Nonvolatile
apply" is much larger than all the other mechanisms.  That mechanism was not
implemented as part of CudeleFS -- it was a debugging and recovery tool packaged
with CephFS. It works by iterating over the updates in the journal and pulling
all objects that {\it may} be affected by the update.  This means that two
objects are repeatedly pulled, updated, and pushed: the object that houses the
experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  The cost of communcating through the object store is shown
by comparing the runtime of ``Volatile apply" + ``Global persist" to
``Nonvolatile Apply". These two operations end up with the same final metadata
state but using ``Nonvolatile Apply" is clearly inferior.

% persist vs. save: one disk vs. many
\subsubsection{Parallelism of the Object Store} Comparing ``Local" and ``Global
persist" demonstrates the bandwidth advantages of storing the journal in a
distributed object store. For 100K file creates, the ``Global Persist"
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the size of the object store can help mitigate the overheads of
globally persisting metadata updates.

\subsubsection{Journal Size} Figure~\ref{fig:behavior-journal-size} shows the
amount of storage per journal update (\(y\) axis) for the range of file creates
we tested (\(x\) axis). The increase in file size is linear with the number of
metadata creates and suggests that updates for a million files would be
\(2.5\text{KB}*1\text{ million files} = 2.38\text{GB}\). Transfer times for
payloads of this size on an HPC network are reasonable.\\

\noindent\textbf{Takeaway}: the CudeleFS mechansisms have overheads and costs
that can differ {\it by order of magnitude}. CudeleFS gives users the ability
to compose these mechanisms based on their application's correctness
requirements and performance goals.

@@

Figure~\ref{fig:slowdown-strong-weak} shows the runtimes of systems employing
weak and strong consistency, normalized to the runtime of the ``Create"
mechanism (again, just creating files in the client's in-memory journal).  We
use the following compositions from the mechanisms in
Table~\ref{table:spectrum}:  Strong Consistency = ``RPCs" + ``Stream"; Strong
Consistency, No Fault Tolerance = ``RPCs"; Weak Consistency = ``Creates" +
``Local Persist"; and Weak Consistency, No Fault Tolerance = ``Creates" +
``Local Persist" + ``Volatile Apply".

@@

% POSIX (no stream) vs. POSIX: cost of durability < consistency
\subsubsection{Durability \(<<\) Consistency} The \(1.15\times\) overhead of
Strong Consistency compared to Strong Consistency, No Fault Tolerance for
100K files is neglible. It suggests that the overhead of consistency is much
larger than the overhead of durability. This conclusion should be stronger as
we scale the number of files because the cost of streaming the journal into the
object store is constant. We omit the same analysis for Weak Consistency
because the runtimes are so short that the normalized slowdowns are misleading.

% Weak Consistency benefit not due to metadata format
\subsubsection{Metadata Formats} Because the metadata formats are the same for
all schemes we argue that the performance gain for decoupled namespaces comes
from relaxing the consistency guarantees and not from the metadata formats, as
was argued in previous work outlining the benefit of
SSTables~\cite{ren:atc2013-tablefs, ren:sc2014-indexfs}.\\

\noindent\textbf{Takeaway}: CudeleFS shows the true benefit of eventual
consistency, where we see over a \(100\times\) slowdown for achieving strong
consistency, in the worst case.

@@

% setup: 2cs sep dirs, 2cs DN, 1c malicious write
Next we show how CudeleFS can be programmed to block interferring clients. We
use the same problematic workload from Figure~\ref{fig:interfere-b}, where
clients write to their own private directories and another client interferes with a stream of creates at
30 seconds.  We also have another client write to a decoupled namespace and
merge its updates at 90 seconds.  We equip each client directory with the
configuration in Listing~\ref{src:block}.  Each directory functions with RPCs
and stream enabled -- which is the default implementation of CephFS. The only
difference is that we enable blocking on each subtree so while the tree behaves
like CephFS, all interferring operations will be returned with \texttt{-EBUSY}.
Note that IndexFS does a similar operation with leases except clients block.

% results
To show the benefits of this isolations, our results in
Figure~\ref{fig:slowdown-allow-block} are plotted alongside the bars from
Figure~\ref{fig:interfere-b}. Because ``allow"/``interfere and
``block"/``isolated" have the same performance we draw the following three
conclusions: (1) clients that use the API to block interferring clients  get
the same performance as isolated clients, (2) there is a neglible effect on
performance for the extra work the metadata server does to return
\texttt{-EBUSY}, and (3) merging updates from the decoupled client has a
neglible effect on performance.\\

\noindent\textbf{Takeaway}: the API lets users isolate directories when
applications need better and more reliable performance. This is a way of
controlling consistency.

@@
